### 2022-03-28 manuscript.tex
tuba [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/c38737afb577e35ec46750d76de1b28f67b86192.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/c38737afb577e35ec46750d76de1b28f67b86192/checks
https://github.com/scherzerthesis/thesis/actions/runs/2053492222

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/811a8b3bb3b4ebbd000e6e5f7822e0778a33601f/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/811a8b3bb3b4ebbd000e6e5f7822e0778a33601f}{scherzerthesis/thesis@811a8b3}
on March 28, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:05}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/c38737afb577e35ec46750d76de1b28f67b86192/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/c38737afb577e35ec46750d76de1b28f67b86192}{scherzerthesis/thesis@c38737a}
on March 28, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.png}
\caption{\textbf{Figure 2.1. Overview of Tuba-Seq experimentation} (A) Lenti-sgRNA-Cre plasmid library with collection of targeted tumor supressors. (B) \emph{Braf\textsuperscript{CAT/+}} and \emph{Braf\textsuperscript{CAT/+};H11b\textsuperscript{LSL-Cas9/+}} were infected with either 10\textsuperscript{4} (16 week \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}}) or 10\textsuperscript{5} (8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} and 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}}) (B) Representative gross images of experimental mouse lungs.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.png}
\caption{**Figure 2.2. Jitter plot of calculated tumor cell number based on Tuba-Seq pipeline. Mean tumor number for 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 21,248 cells. Mean tumor number for 8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 9,095 cells. Mean tumor number for 16 week \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 29,867 cells.}\label{fig:05}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.png}
\caption{\textbf{Figure 2.3. Jitter plot of calculated tumor cell number based on Tuba-Seq pipeline seperated by sgID. (A) 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}}(negative control) has no apparent cooperative genetic events. (B)8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} identifed Apc loss as a cooperating genetic event based on increase in tumor cell number (C) This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}
